---
title: "Reproducible document"
author: "Julian Bjerrekaer"
format: html
---

## Basics of R

```{r}
1 + 1
```

## About me

- Julian Bjerrekær
- Steno Diabetes Center
- University of Copenhagen

I am an **old** man. I live in *Copenhagen*.

```{r}
3 * 3
```
## Testing for Git

The weather was sunny today.

## Setup code chunk

```{r setup}
#| message: false
#| warning: false
library(tidyverse)
post_meal_data <- read_csv2(
  here::here("data/post-meal-insulin.csv")
)
```

## Showing the data

```{r}
post_meal_data
```

```{r}
glimpse(post_meal_data)
```

```{r}
ggplot(post_meal_data, aes(x = BMI)) +
geom_histogram()
```

```{r}
#| fig-cap: "Distribution of BMI"
#| label: fig-bmi-histo
#| message: false
ggplot(post_meal_data, aes(x = BMI)) +
geom_histogram()
```

@fig-bmi-histo

## Exercise: discrete plots.

```{r}
#| fig-cap: "Distribution of glycemia"
#| label: fig-glykemi-bar
ggplot(post_meal_data, aes(x = glykemi)) +
  geom_bar()
```

See @fig-glykemi-bar above for a cool plot!

```{r}
post_meal_data |>
  ggplot(aes(x = Group, fill = glykemi)) + 
  geom_bar()
```

```{r}
post_meal_data |>
  ggplot(aes(x = Group, fill = as.character(glykemi))) + 
  geom_bar()

```

```{r}
post_meal_data |>
  ggplot(aes(x = Group, fill = as.character(glykemi))) + 
  geom_bar(position = position_dodge())

```

## Putting two plots side by side

```{r}
ggplot(post_meal_data, aes(x = BMI)) +
  geom_histogram()
```

```{r}
  ggplot(post_meal_data, aes(x = glykemi)) +
  geom_bar()
```

```{r side-by-side-figs}
#| label: fig-bmi-glykemi
#| message: false
#| fig-cap: "BMI Kand Glykemi, side by side"
#| fig-subcap: 
#| - "Distribution of BMI"
#| - "Distribution of glycemia"
#| layout-ncol: 2

ggplot(post_meal_data, aes(x = BMI)) +
  geom_histogram()

ggplot(post_meal_data, aes(x = glykemi)) +
  geom_bar()
```

## Plotting two continuous variables 

```{r}
  ggplot(post_meal_data, aes(x = BMI, y = auc_pg)) +
  geom_point()
```

```{r}
#| message: false
#| fig-cap: "scatterplot showing BMI against AUC of blood glucose"
#| label: fig-bmi-auc-pg
 ggplot(post_meal_data, aes(x = BMI, y = auc_pg)) +
  geom_point() +
  geom_smooth()
```

@fig-bmi-auc-pg

usethis::create_github_token()

